### 2019-03-21 6_related.tex
More related work.

>>>>

System-specific benchmarks have been used to quantify specific aspects
of system performance, such as MPI communication or collective
latency~\cite{MPPTest99, MPIBench01}. These measurements typically do
not generalize beyond the immediate system they attempt to quantify,
nor in an obvious way to real-world applications.

Limit studies of task scheduling throughput in various runtime systems
often make additional assumptions. A popular assumption is the use of
trivially parallel tasks~\cite{Canary16, Armstrong14}, which as shown
in Section~\ref{subsec:number-of-dependencies} underestimates (often
substantially) the cost of scheduling a task. Worse, trivial
parallelism overstates the scalability of the runtime system; our
results for Swift/T in Section~\ref{subsec:scalability} differ rather
substantial from those published in~\cite{Armstrong14} for this
reason.
